---
title: Home Range Analysis Assignment <br><small>Advanced Data Analytics</small></br>
author: Nate Selleck
output:
  html_document: 
    df_print: paged
    rows.print: 10
    theme: cosmo
    highlight: breezedark
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document: default
  html_notebook:
    df_print: paged
    rows.print: 10
    theme: cosmo
    highlight: breezedark
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
editor_options:
  chunk_output_type: inline
  mode: gfm
---

```{=html}
<style type="text/css">

h1.title {
  font-size: 40px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}

h4.author { /* Header 4 - and the author and data headers use this too  */
  font-size: 25px;
  font-family: "Times New Roman", Times, serif;
  font-weight: bold;
  color: #D02349;
  text-align: center;
}

body {
  font-family: Helvetica;
  font-size: 12pt;
}

.zoom {
  transform-origin: 40% 50% 0;
  transition: transform .2s;
  margin: 0 auto;
}
.zoom img{
	width:auto;
	height:auto;	
}
.zoom:hover {
  transform: scale(2);
}

th, td {padding: 5px;}

</style>
```


<body style = "background-color:#b1d3aa">



```{r Packages, echo=TRUE, message=FALSE, warning=FALSE}
pacman::p_load("adehabitatHR","data.table","ggfortify","OpenStreetMap","grid","move","moveVis","OpenStreetMap","pbapply","maptools","rgdal","plotly","sp","tidyverse","viridis")

```


# Import Data Set

This is the same data set used for the Basic Mapping assignment. These GPS points were collected for three Louisiana Waterthrush territories at Cheatham Wildlife Management Area in Cheatham Co, TN. For the purpose of getting a later line of code to work, I changed the ID's for each bird to LOWA1-LOWA3. 
```{r data, echo=TRUE, message=FALSE, warning=FALSE}
data <- read.csv("./Data/lowa_location_data.csv")
```

```{r structure, echo=TRUE, message=FALSE, warning=FALSE}
head(data)
```
# QAQC Plot

```{r plotly, echo=TRUE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
qaqc_plot <- ggplot() + geom_point(data=data, 
                                   aes(Easting,Northing,
                                       color=ï..id)) +
                        labs(x="Easting", y="Northing") +
                        guides(color=guide_legend("Identifier"))

ggplotly(qaqc_plot)
```

 

```{r lapply function, echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
lapply(split(data, data$ï..id), 
       function(x)write.csv(x, file = paste(x$ï..id[1],".csv", sep = ""), row.names = FALSE))
```



```{r list, echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
files <- list.files(path = ".", pattern = "[LOWA]+[0-9]+", full.names = TRUE)
```



```{r imagery, message=FALSE, warning=FALSE, echo=TRUE, fig.height=6, fig.width=8}
utm_points <- cbind(data$Easting, data$Northing)
utm_locations <- SpatialPoints(utm_points, 
                 proj4string=CRS("+proj=utm +zone=16 +datum=WGS84"))
proj_lat.lon <- as.data.frame(spTransform(
                utm_locations, CRS("+proj=longlat +datum=WGS84")))
colnames(proj_lat.lon) <- c("x","y")
raster <- openmap(c(max(proj_lat.lon$y)+0.01, min(proj_lat.lon$x)-0.01), 
                  c(min(proj_lat.lon$y)-0.01, max(proj_lat.lon$x)+0.01), 
                  type = "bing")
raster_utm <- openproj(raster, 
              projection = "+proj=utm +zone=16 +datum=WGS84 +units=m +no_defs")
```


$~$

# Plot the Data

```{r imagery plot, message=FALSE, warning=FALSE, echo=TRUE, fig.height=6, fig.width=6}
autoplot.OpenStreetMap(raster_utm, expand = TRUE) + theme_bw() +
  theme(legend.position="bottom") +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  geom_point(data=data, aes(Easting,Northing,
             color=ï..id), size = 3, alpha = 0.8) +
  theme(axis.title = element_text(face="bold")) + labs(x="Easting",
        y="Northing") + guides(color=guide_legend("Identifier"))
```

$~$

# Minimum Convex Plygon

```{r MCP plot, message=FALSE, warning=FALSE, echo=TRUE, fig.height=6, fig.width=6}
mcp_raster <- function(filename){
  data <- read.csv(file = filename)
  x <- as.data.frame(data$Easting)
  y <- as.data.frame(data$Northing)
  xy <- c(x,y)
  data.proj <- SpatialPointsDataFrame(xy,data, proj4string = CRS("+proj=utm +zone=16 +datum=WGS84 +units=m +no_defs"))
  xy <- SpatialPoints(data.proj@coords)
  mcp.out <- mcp(xy, percent=100, unout="ha")
  mcp.points <- cbind((data.frame(xy)),data$ï..id)
  colnames(mcp.points) <- c("x","y", "identifier")
  mcp.poly <- fortify(mcp.out, region = "id")
  units <- grid.text(paste(round(mcp.out@data$area,2),"ha"), x=0.85,  y=0.95,
                     gp=gpar(fontface=4, col="white", cex=0.9), draw = FALSE)
  mcp.plot <- autoplot.OpenStreetMap(raster_utm, expand = TRUE) + theme_bw() + theme(legend.position="none") +
    theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    geom_polygon(data=mcp.poly, aes(x=mcp.poly$long, y=mcp.poly$lat), alpha = 0.5, fill = "red") +
    geom_point(data=mcp.points, aes(x=x, y=y)) + 
    labs(x="Easting (m)", y="Northing (m)", title=mcp.points$identifier) +
    theme(legend.position="none", plot.title = element_text(face = "bold", hjust = 0.5)) + 
    annotation_custom(units)
  mcp.plot
}

pblapply(files, mcp_raster)
```

$~$

# Kernel Density Estimate

```{r KDE plot, message=FALSE, warning=FALSE, echo=TRUE, fig.height=6, fig.width=6}
kde_raster <- function(filename){
  data <- read.csv(file = filename)
  x <- as.data.frame(data$Easting)
  y <- as.data.frame(data$Northing)
  xy <- c(x,y)
  data.proj <- SpatialPointsDataFrame(xy,data, proj4string = CRS("+proj=utm +zone=16 +datum=WGS84 +units=m +no_defs"))
  xy <- SpatialPoints(data.proj@coords)
  kde<-kernelUD(xy, h="href", kern="bivnorm", grid=100)
  ver <- getverticeshr(kde, 95)
  kde.points <- cbind((data.frame(data.proj@coords)),data$ï..id)
  colnames(kde.points) <- c("x","y","identifier")
  kde.poly <- fortify(ver, region = "id")
  units <- grid.text(paste(round(ver$area,2)," ha"), x=0.85,  y=0.95,
                     gp=gpar(fontface=4, col="white", cex=0.9), draw = FALSE)
  kde.plot <- autoplot.OpenStreetMap(raster_utm, expand = TRUE) + theme_bw() + theme(legend.position="none") +
    theme(panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    geom_polygon(data=kde.poly, aes(x=kde.poly$long, y=kde.poly$lat), alpha = 0.5, fill = "red") +
    geom_point(data=kde.points, aes(x=x, y=y)) +
    labs(x="Easting (m)", y="Northing (m)", title=kde.points$identifier) +
    theme(legend.position="none", plot.title = element_text(face = "bold", hjust = 0.5)) + 
    annotation_custom(units)
  kde.plot
}

pblapply(files, kde_raster)
```

The three KDE maps have large buffers and aren't very accurate, mostly due to the low number of data points to work from. 
